\Large{Adversarial Training against Systematic Uncertainty}

### 2016-10-27 tex/paper.tex
save

Jets, or collimated sprays of particles produced by high energy quarks and
gluons, are produced ubiquitously at high energy colliders like the Large Hadron
Collider \citep{LHCMachine}.  In a wide array of new physics models, new highly
massive particles can decay though known heavy particles in Standard Model (SM),
like the $W$, $Z$, Higgs bosons, or top quarks which subsequently decay to
multiple quarks.  When these these heavy SM particles have significant energy,
the Lorentz boost causes their quark decay products to merge into a single jet
which has a rich internal substructure (see e.g.
\citep{Altheimer:2012mn,Altheimer:2013yza} and references therein).
Distinguishing these \textit{boosted jets} produced by heavy SM particles from
vanilla quarks and  gluons is a fundamental challenge in searching for signs of
new high mass particles. Challenging in it's own right, this classification
problem is made all the more difficult by the presence of pileup, or multiple
simultaneous proton-proton interactions occurring at the same time as the primary
interaction.  These pileup interactions produce additional particles that can
contribute significant energies to jets unrelated to the underlying
discriminating information. Thus pileup acts as a source of noise in the
classification problem.

>>>>

Jets, or collimated sprays of particles produced by high energy quarks and
gluons, are produced ubiquitously at high energy colliders like the LHC \citep{LHCMachine}.
In a wide array of new physics models, new highly
massive particles can decay through known heavy particles in the Standard Model (SM),
like the $W$, $Z$, Higgs bosons, or top quarks which subsequently decay to
multiple quarks.  When these heavy SM particles have significant energy,
the Lorentz boost causes their quark decay products to merge into a single jet
which has a rich internal substructure (see e.g.
\citep{Altheimer:2012mn,Altheimer:2013yza} and references therein).
Distinguishing these boosted jets produced by heavy SM particles from
vanilla quarks and  gluons is a fundamental challenge in searching for signs of
new high mass particles. Challenging in its own right, this classification
problem is made all the more difficult by the presence of pileup, or multiple
simultaneous proton-proton interactions occurring at the same time as the primary
interaction.  These pileup interactions produce additional particles that can
contribute significant energies to jets unrelated to the underlying
discriminating information. Thus pileup acts as a source of noise in the
classification problem.
